Relational Presentations Using Semantic Closeness\\Spatial Narrative for Mathematical Content

### 2015-06-13 Paper.tex
fixed dimensions of images'

\begin{wrapfigure}l{.65\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.63\textwidth]{assets/final/inclusionGraphPythagorean}} 
  \vspace{-1.8em}
  \caption{Pythagorean Theorem Inclusion Graph}\label{fig:inclusionGraph}
  \vspace{-2em}
\end{wrapfigure}

@@

As described in \autoref{sec:TowardsAMoreEffectivePresentationFormat}, lmh outputs information about dependencies of topics. \sys parses this relational data and retrieves the dependencies of the topics which are visualized for Annie's example in \autoref{fig:depGraphPythagoreanFull}. Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information obtained longer ago.

\begin{figure}[ht]\vspace{-1em}
  \fbox{\includegraphics[width=0.97\textwidth]{assets/final/dependencyGraphPythTheo2}} 
  \vspace{-.5em}
  \caption{Dependency Graph}\label{fig:depGraphPythagoreanFull}
\end{figure}

\begin{wrapfigure}r{.67\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.67\textwidth]{assets/final/fullPresentation2}} 
  \vspace{-1.8em}
  \caption{Visualization of Dependencies}\label{fig:visualDependency}
  \vspace{-2em}
\end{wrapfigure}
With the data about the order and the dependencies of information within the paper, we now
have an ordered information graph out of which we can build a first presentation that
Annie can interact with to learn about the Pytha\-go\-rean theorem. \sys creates this
presentation incrementally. As outlined in \autoref{sec:narrativePaths}, \sys creates the primary narrative path from the order
of the slides. After adding each slide it checks whether there is \textit{course-ancient}
information, i.e. whether there are dependencies, for that slide. If there are
dependencies those are added below the slide itself (see
\autoref{fig:visualDependency}).\footnote{The library impress.js was adapted to support the
  choosing of different paths by pressing the right or down key
  \cite{npentrel:npentrel15}.}

@@

\begin{wrapfigure}r{.63\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.6\textwidth]{assets/final/levels}} 
  \vspace{-0.8em}
  \caption{Inclusion Graph with Levels}\label{fig:levelsGraph}
\vspace{-2em}
\end{wrapfigure}
When writing a document or course notes in \stex, the creator general writes a top-level
file such as \textit{notes.tex} from where other \TeX\ files are included. These included
files again include further \TeX\ files etc.. Thus we are automatically provided with
levels that we can use for splicing our primary narrative path into smaller narrative
paths. In essence, on any level the order of information in that topic is a narrative path
itself. Expressed in mathematical notation a level within a directed graph
$G = \langle V, E \rangle $, with $V$ being a set of nodes and $E = V \times V$ being the
set of directed edges, is the set
$L_w = \lbrace v \vert \langle w, v \rangle \in E \rbrace$. From these levels we can infer
the status of the information. We already know that a dependent piece of information
infers that it is \textit{course-ancient} information. Anything that is on the same level
or in the sublevels thereof is considered to be \textit{course-old} information.

>>>>

\begin{figure}[ht]\vspace{-1.5em}
  \fbox{\includegraphics[width=1\textwidth]{assets/final/inclusionGraphPythagorean}} 
  \vspace{-1.5em}
  \caption{Pythagorean Theorem Inclusion Graph}\label{fig:inclusionGraph}
\vspace{-2em}
\end{figure}

@@

\begin{wrapfigure}l{.42\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.40\textwidth]{assets/final/pythdep2}} 
  \vspace{-1.9em}
  \caption{Dependency Graph}\label{fig:depGraphPythagoreanFull}
  \vspace{-2em}
\end{wrapfigure}
As described in \autoref{sec:TowardsAMoreEffectivePresentationFormat}, lmh outputs information about dependencies of topics. \sys parses this relational data and retrieves the dependencies of the topics which are visualized for Annie's example in \autoref{fig:depGraphPythagoreanFull}. Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information obtained longer ago.

With the data about the order and the dependencies of information within the paper, we now
have an ordered information graph out of which we can build a first presentation that
Annie can interact with to learn about the Pytha\-go\-rean theorem. \sys creates this
presentation incrementally. As outlined in \autoref{sec:narrativePaths}, \sys creates the primary narrative path from the order
of the slides. After adding each slide it checks whether there is \textit{course-ancient}
information, i.e. whether there are dependencies, for that slide. If there are
dependencies those are added below the slide itself (see
\autoref{fig:visualDependency}).\footnote{The library impress.js was adapted to support the
  choosing of different paths by pressing the right or down key
  \cite{npentrel:npentrel15}.}

\begin{figure}[ht]\vspace{-1.5em}
  \fbox{\includegraphics[width=1\textwidth]{assets/final/fullPresentation2}} 
  \vspace{-1.5em}
  \caption{Visualization of Dependencies}\label{fig:visualDependency}
\vspace{-2em}
\end{figure}

@@

When writing a document or course notes in \stex, the creator general writes a top-level
file such as \textit{notes.tex} from where other \TeX\ files are included. These included
files again include further \TeX\ files etc.. Thus we are automatically provided with
levels that we can use for splicing our primary narrative path into smaller narrative
paths. In essence, on any level the order of information in that topic is a narrative path
itself. Expressed in mathematical notation a level within a directed graph
$G = \langle V, E \rangle $, with $V$ being a set of nodes and $E = V \times V$ being the
set of directed edges, is the set
$L_w = \lbrace v \vert \langle w, v \rangle \in E \rbrace$. From these levels we can infer
the status of the information. We already know that a dependent piece of information
infers that it is \textit{course-ancient} information. Anything that is on the same level
or in the sublevels thereof is considered to be \textit{course-old} information.

\begin{figure}[ht]\vspace{-1.5em}
  \fbox{\includegraphics[width=1\textwidth]{assets/final/levels}} 
  \vspace{-1.5em}
  \caption{Inclusion Graph with Levels}\label{fig:levelsGraph}
\vspace{-2em}
\end{figure}
